\documentclass[margin,line]{res}

\usepackage{color}
\usepackage{etaremune}

\usepackage{hyperref}

\newcommand{\linkToUrl}[1]{\underline{\color{blue} \href{#1}{Link}}}


%uncomment for printed copy:
%\renewcommand{\linkToUrl}[1]{}

\oddsidemargin -.5in
\evensidemargin -.5in

%uncomment if trying to squeeze a bit more on to a page
\textheight 9.5in 

\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}


\name{Todd Bodnar \vspace*{.1in} \   ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  \normalfont \footnotesize Last edited 5/20/2013}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{4.35in}p{4in} }
     & Updated CV on \underline{\color{blue} \href{http://bit.ly/12hkTV3}{GitHub}}  \\             %email me if you need my phone number
\   &  {\it E-mail:}  \(^{}\)me\(m\)e@p\(^{}\)su\(_{^*}\)\(^{}\)edu \\         %generic antispam attempt, cool eh?
\end{tabular}


\section{\sc Research Interests}
Social networks, computational modeling, game theory, data mining
\ \\
\section{\sc Degrees}
{\bf Pennsylvania State University}, State College, Pennsylvania USA\\
\vspace*{-.1in}
\begin{list1}
\item[] PhD, Biology, 2016 (Expected)
\item[] Advisor: Marcel Salath\'e
\end{list1}
{\bf Pennsylvania State University} \\
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Computer Science,  May, 2012 
\item[] Junior/Senior GPA 3.90
\item[] Minor in Mathematics
\end{list1}

\section{\sc Academic \\Related Experience}
Research with the Salath\'e Group% (September 2010 - Present)
\begin{list1}
\item[] PhD advisor
%\item[] Visualized / Analyzed graphs from Twitter data
%\item[] Developed behavioral models
\end{list1}
Complex Systems Summer School (CSSS) at Santa Fe Institute. (June 3-28, 2013)

Grader for Cmpsc 464 (January 2012 - April 2012)
\begin{list1}
\item[] Graded homework for the senior level class: ``Introduction to the Theory of Computation''
\item[] Topics covered include automata, Turing machines and complexity.
\end{list1}
Undergraduate research with Dr. Eric Charles% (April 2010 - August 2010)
\begin{list1}
\item[] Penn State psychology department.
\item[] Developed models for modified prisoner's dilemma games (MOTH).
\item[] Developed Map-Reduce mod for running NetLogo simulations on multiple computers. \linkToUrl{http://bit.ly/12UQ4cq}
\end{list1}
%\section{\sc Honors and Awards}

%Braddock Award (Fall 2012)

%Deans List (Fall 2009 - Present)

%\section{\sc Research Experience}

\section{\sc Publications}

\begin{etaremune}[start=3]

\item \textbf{Todd Bodnar} \& Marcel Salath\'e. \textit{Validating Models for Disease Detection Using Twitter}  WWW 2013 Companion, May 13-17, 2013, Rio de Janeiro, Brazil. \linkToUrl{http://bit.ly/WWL1Gr}

\item Marcel Salath\'e, Linus Bengtsson, \textbf{Todd J. Bodnar}, Devon D. Brewer, John S. Brownstein, Caroline Buckee, Ellsworth M. Campbell, Ciro Cattuto, Shashank Khandelwal, Patricia L. Mabry,  Alessandro Vespignani. \textit{Digital Epidemiology} Plos Computational Biology, 2012 \linkToUrl{http://bitly.com/PO2fSx}

\item \textbf{Todd Bodnar} \& Marcel Salath\'e. \textit{Governing the Global Commons with Local Institutions}. PloS One, 2012 \linkToUrl{http://bit.ly/TtsZd5}
\end{etaremune}

%\section{\sc Presented Papers and Posters}
\section{\sc Presentations}
\begin{etaremune}[start=3]
\item Todd Bodnar. \textit{Arbortrons.} Santa Fe Institute, 2013
\item Todd Bodnar. \textit{Processing Big-Data for Cheap through Amazon's Elastic Map Reduce.} Hacking Science Seminar, 2013
%\item Todd Bodnar. \textit{Complex Models and Over-fitting}. Bring your own data problems, Hacking Science, 2012 (Short, 5 minute talk)
\item Todd Bodnar, Orhan Kislal, Ying Sun, Hui Yang,Marcel Salath\'e, Conrad 
Tucker. \textit{Webs, Clouds and Tweets: Using Social Media to Study the Spatial Dynamics of Influenza}. Center for Integrated Healthcare Delivery Systems, 2012 
\end{etaremune}


%comment out from here
%\ 
%
%\section{\sc Conferences, Workshops, etc. Attended}
%\begin{etaremune}[start=5]
%\item 2013 June 3-28: Complex Systems Summer School (CSSS) at Santa Fe Institute. (Upcoming)
%\item 2013 May 14:1st International Workshop on Public Health in the Digital Age: Social Media, Crowdsourcing and Participatory Systems (held in conjunction with WWW 2013) (Upcoming)
%\item 2013 May 13-17: 22nd International World Wide Web Conference (WWW 2013). Rio de Janeiro. (Upcoming)
%\item 2012 April 5: 4th Center for Integrated Healthcare Delivery System Workshop. Pennsylvania State University.
%\item 2010 July 2-3: North American Meeting of the International Society for Ecological Psychology. Illinois State University.
%\end{etaremune}
%to here for short version of cv

\section{\sc Software}
Crowdbreaks \linkToUrl{http://www.crowdbreaks.com}
\begin{list1}
\item[] Online disease surveillance system using social media.
\item[] Worked on backend, developed system for fast processing of large geospatial data sets.


\end{list1}

\section{\sc Computer Skills} 
\begin{list2}
\item Cluster Computing / Hadoop 
\item Web based psychological game development on Amazon Mechanical Turk
\item General software development / programing
\item \LaTeX
\end{list2}

%\section{\sc Miscellaneous Information}
%\begin{list2}
%\item Native language: English
%\item Understands some French
%\item U.S. citizen
%\end{list2}



\end{resume}
\end{document}




